THESIS PROJECT PROPOSAL

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

The production of Higgs boson in association with single top quark is one of the rare Higgs boson production mode. As the top 
quark is the heaviest fundamental particle in the standard model, due to its large mass, the top quark decay before 
hardronization which allow the possibility to reconstruct top quark from its decay products unlike the lighter quarks which 
undergo hardronization and are seen as bundles of particles in detector called jets. The most probable decay of top quark is into 
bottom(b) quark and W boson. Using b-jet tagging algorithms, the jet originating from b-quark can be reconstructed to identity 
the top quark. In SM, the coupling of the Higgs boson to fermions is proportional to the mass of the fermions. Thus heavy quarks 
like top, bottom and charm couple strongly to Higgs boson which means that out of all known quarks, top quark couple most 
strongly to the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa coupling of the top quark 
with the Higgs boson Y_t has lot of importance as any deviation from standard model prediction might give an indication of new 
physics. The two processes at LHC which will allow us to directly probe the Yukawa coupling between Higgs Boson and top 
quark are Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and the production 
of single top quark with a Higgs boson(tH). As tH occur via electroweak interaction, it is more rare than t\bar{t}H production.

>>>>

The production of Higgs boson in association with single top quark is one of the rare Higgs boson production mode. As the top 
quark is the heaviest fundamental particle in the standard model, due to its large mass, the top quark decay before 
hardronization which allow the possibility to reconstruct top quark from its decay products unlike the lighter quarks which 
undergo hardronization and are seen as bundles of particles in detector called jets. The most probable decay of top quark is into 
bottom(b) quark and W boson. Using b-jet tagging algorithms, the jet originating from b-quark can be reconstructed to identity 
the top quark. In SM, the coupling of the Higgs boson to fermions like quarks and leptons is proportional to the mass of the 
fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson which means that out of all known quarks, 
top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa 
coupling of the top quark with the Higgs boson Y_t has lot of importance as any deviation from standard model prediction might 
give an indication of new physics. The two processes at LHC which will allow us to directly probe the Yukawa coupling between 
Higgs Boson and top quark are Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and 
the production of single top quark with a Higgs boson(tH). As tH occur via electroweak interaction, it is more rare than 
t\bar{t}H production. The Higgs boson in the tH channel can be radiated off by a W boson or by a top quark. These two processes in standard model have destructive interference which allow us to probe the relative sign between the coupling of top quark with Higgs boson Y_t and the coupling of W boson to the Higgs boson.
